---
title: "Regression Output in Tables for a PDF"
author: "Christopher Gandrud"
date: "8 November 2014"
output: pdf_document
bibliography: Rpackages.bib
---

```{r, include=FALSE}
pkgs <- c('knitr', 'stargazer')
repmis::LoadandCite(pkgs, file = 'Rpackages.bib')
```

This is a document showing how to automatically generate tables for showing
regression output. The first part shows how to Create tables from data frames
with the `kable` function in the knitr package [@R-knitr]. The second part shows how to use
the stargazer package [@R-stargazer]. 

**Note** this version of the document is for creating tables in R Markdown that
is **compiled to PDF**.

Both examples use data from [UCLA IRDE](http://www.ats.ucla.edu/stat/). To 
access the data use:

```{r}
URL <- 'http://www.ats.ucla.edu/stat/data/binary.csv'
Admission <- read.csv(URL)
```

## `kable` for creating tables from data frames

Imagine that we want to create a table of predicted probabilities from a 
logistic regression model. First we simply run our model and create our 
predicted probabilities:

```{r}
# Estimate model
Logit1 <- glm(admit ~ gre + gpa + as.factor(rank),
              data = Admission, family = 'binomial')

# Create scenario labels
Scenarios <- c('Scenario 1', 'Scenario 2', 'Scenario 3', 'Scenario 4')

# Create fitted data
fitted <- with(Admission,
               data.frame(gre = mean(gre),
                          gpa = mean(gpa),
                          rank = factor(1:4)))
# Predict probabilities
fitted$predicted <- predict(Logit1, newdata = fitted,
                            type = 'response')

# Combine
fitted <- data.frame(Scenarios, fitted)
```

Then we simply pass the `fitted` object to the `kable` function to create our 
table of predicted probabilities.

```{r, results='asis'}
knitr::kable(fitted, align = 'c', digits = 2,
      caption = 'Predicted Probabilities for Fitted Values')
```

## stargazer for creating tables from model output objects

If you want to automatically generate tables from regression model output
objects, texreg is a good package to turn to. First estimate your models:

```{r}
L1 <- glm(admit ~ gre,
              data = Admission, family = 'binomial')

L2 <- glm(admit ~ gre + gpa,
              data = Admission, family = 'binomial')

L3 <- glm(admit ~ gre + gpa + as.factor(rank),
              data = Admission, family = 'binomial')
```

Then use the stargazer function to create a results table. For PDFs set 
`type = 'latex'`. There are many stylistic
modifications you can make with this function.

```{r, message=FALSE, results='asis'}
# Create custom clean coefficient labels
labels <- c('(Intercept)', 'GRE Score', 'GPA Score', '2nd Ranked School',
            '3rd Ranked School', '4th Ranked School')
stargazer::stargazer(L1, L2, L3, covariate.labels = labels,
               title = 'Logistic Regression Estimates of Grad School Acceptance',
               type = 'latex', header = FALSE)
```

## References